The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the OVRO-LWA

### 2018-07-06 paper.tex
add corrections from the editor

\begin{abstract}
    A host of new low-frequency radio telescopes seek to measure the 21-cm transition of neutral
    hydrogen from the early universe.  These telescopes have the potential to directly probe star
    and galaxy formation at redshifts $20 \gtrsim z \gtrsim 7$, but are limited by the dynamic range
    they can achieve against foreground sources of low-frequency radio emission. Consequently, there
    is a growing demand for modern, high-fidelity maps of the sky at frequencies below 200 MHz for
    use in foreground modeling and removal.  We describe a new widefield imaging technique for
    drift-scanning interferometers, Tikhonov-regularized $m$-mode analysis imaging.  This technique
    constructs images of the entire sky in a single synthesis imaging step with exact treatment of
    widefield effects.  We describe how the CLEAN algorithm can be adapted to deconvolve maps
    generated by $m$-mode analysis imaging. We demonstrate Tikhonov-regularized $m$-mode analysis
    imaging using the Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA) by generating
    8 new maps of the sky north of $\delta=-30^\circ$ with 15 arcmin angular resolution, at
    frequencies evenly spaced between 36.528~MHz and 73.152~MHz, and $\sim$800 mJy/beam thermal
    noise. These maps are a 10-fold improvement in angular resolution over existing full-sky maps at
    comparable frequencies, which have angular resolutions $\ge 2^\circ$. Each map is constructed
    exclusively from interferometric observations and does not represent the globally averaged sky
    brightness. Future improvements will incorporate total power radiometry, improved thermal noise,
    and improved angular resolution -- due to the planned expansion of the OVRO-LWA to 2.6~km
    baselines.  These maps serve as a first step on the path to the use of more sophisticated
    foreground filters in 21-cm cosmology incorporating the measured angular and frequency structure
    of all foreground contaminants.
\end{abstract}

@@

At redshifts $20 \gtrsim z \gtrsim 7$, the 21-cm hyperfine structure line of neutral hydrogen is
expected to produce a 10 to 100 mK perturbation in the Cosmic Microwave Background (CMB) spectrum
\citep{2006PhR...433..181F, 2012RPPh...75h6901P}. The amplitude of this perturbation on a given
line-of-sight is a function of the neutral fraction of hydrogen, the baryon overdensity, the spin
temperature relative to the CMB temperature at the given redshift, and the line-of-sight peculiar
velocity of the gas.  The spatial power spectrum of this perturbation is thought to be dominated by
inhomogeneous heating of the IGM at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing ionized
bubbles during the EoR at $z\sim 7$ where a detection can constrain the ionizing efficiency of early
galaxies, the UV photon mean-free-path, and the minimum halo mass that can support star formation
\citep{2015MNRAS.449.4246G}.

Current 21-cm cosmology experiments can be broadly separated into two classes: global signal
experiments that aim to detect the spectral signature of the cosmologically redshifted 21-cm
transition after averaging over the entire sky (otherwise known as the monopole), and power spectrum
experiments that incorporate angular information to attempt to measure the 3D spatial power spectrum
of cosmological 21-cm perturbations.  Ongoing global signal experiments include EDGES
\citep{2017ApJ...847...64M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS \citep{2015PASA...32....4S},
SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2 \citep{2017arXiv170306647S}.  Ongoing power spectrum
experiments include PAPER/HERA \citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR
\citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B, 2016MNRAS.460.4320E}. Recently,
EDGES reported the first detection of 21-cm absorption in the globally averaged sky-signal
\citep{2018Natur.555...67B}.

Just as for CMB experiments, foreground removal or suppression is an essential component of both
classes of 21-cm cosmology experiments. The brightness temperature of the galactic synchrotron
emission at high galactic latitudes is measured by \citet{2017MNRAS.464.4995M} as
\begin{equation}
    T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.6}\,.
\end{equation}
Therefore, experiments conservatively need to achieve 5 orders of dynamic range against this
foreground emission before the cosmological signal can be measured. Current foreground removal
methods (for example, \citealt{2012ApJ...756..165P} and \citealt{2013MNRAS.429..165C}) rely on the
assumption that the foreground emission is spectrally smooth. The low-frequency radio sky is
composed of several components: galactic synchrotron emission, supernova remnants, radio galaxies,
free-free emission and absorption from \ion{H}{2} regions, and a confusing background of radio
sources.  Ideally, a foreground removal strategy should be informed by the measured spatial
structure and frequency spectrum of all foreground components. For instance, CMB experiments
typically construct several maps at several frequencies to enable component separation.  At low
frequencies, this possibility is limited by the availability of suitable high-fidelity sky maps on
angular scales ranging from tens of degrees to arcminutes.

Recently, a host of new low-frequency sky surveys have been conducted including MSSS
\citep{2015A&A...582A.123H}, GLEAM \citep{2015PASA...32...25W}, and TGSS
\citep{2017A&A...598A..78I}. However, the primary data product generated by these surveys is a
catalog of radio point sources. At 45 MHz, \citet{2011A&A...525A.138G} created a map of the sky that
captures the diffuse emission with 5$^\circ$ resolution.  The LWA1 Low Frequency Sky Survey
\citep{2017MNRAS.469.4537D} similarly maps the sky at a range of frequencies between 35~MHz and
80~MHz with resolution between 4.5$^\circ$ and 2$^\circ$.

The Global Sky Model (GSM) \citep{2008MNRAS.388..247D} is currently the most commonly used
foreground model. The GSM is a non-parametric interpolation of various maps between 10 MHz and 100
GHz. However, the majority of information contained in the GSM is derived at frequencies $>1.4$ GHz
where the majority of the modern, high-fidelity input maps are located. At 408~MHz the venerable
Haslam map \citep{1981A&A...100..209H, 1982A&AS...47....1H} covers the entire sky at $1^\circ$
resolution.  Below 408~MHz the GSM uses 3 input sky maps. \citet{2017MNRAS.464.3486Z} construct an
improved GSM with 5 maps below 408~MHz, and \citet{2017MNRAS.469.4537D} use the LWA1 to improve the
GSM with their own sky maps.  However, the GSM generally suffers from low angular resolution ($\sim
5^\circ$) and systematic errors associated with instrumental artifacts in the input maps.  For
instance, \citet{2017MNRAS.469.4537D} report errors of $\pm 50\%$ between the GSM and their own maps
at 74 MHz, which they attribute to the increasing contribution of free-free absorption and
modifications to the synchrotron spectral index at low frequencies.

Widefield interferometric synthesis imaging is a challenging computational problem, and it has been
particularly difficult to capture large angular scales $\gg 10^\circ$ and small angular scales $\ll
1^\circ$ in a single synthesis image. We will derive a new imaging technique -- Tikhonov regularized
$m$-mode analysis imaging -- that allows a drift-scanning interferometer to image the entire visible
sky in a single coherent synthesis imaging step with no gridding and no mosaicking.

As a demonstration of this technique we apply Tikhonov regularized $m$-mode analysis imaging to the
Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA), and generate a series of new
low-frequency maps of the sky between 36.528~MHz and 73.152~MHz.  These maps capture the full sky
visible from the Owens Valley Radio Observatory (OVRO) with angular resolution of $\sim 15$~arcmin.
These new maps complement the existing full-sky maps at these frequencies with greatly improved
angular resolution.

We aim for these maps to inform foreground removal strategies in 21-cm cosmology, and we anticipate
additional ancillary science taking advantage of the combination of high fidelity and high
resolution of these maps, including but not limited to studies of the cosmic ray emissivity at low
frequencies, searches for giant radio galaxies, and constraining the galactic synchrotron spectrum.
The maps will be made freely available online at the Legacy Archive for Microwave Background Data
Analysis (LAMBDA)\footnote{
    \url{https://lambda.gsfc.nasa.gov/product/foreground/fg_ovrolwa_radio_maps_info.cfm}
}.

The structure of this paper is as follows. In \S\ref{sec:imaging}, we present Tikhonov-regularized
$m$-mode analysis imaging, a new imaging technique that allows us to image the entire visible sky in
one coherent synthesis imaging step with exact widefield corrections. In \S\ref{sec:observations} we
describe our observations with the OVRO-LWA. In \S\ref{sec:results} we present the sky maps and
compare these maps against other low-frequency sky maps.  In \S\ref{sec:error} we discuss some of
the sources of error present in the maps, and finally in \S\ref{sec:conclusion} we present our
conclusions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{All-Sky Imaging}\label{sec:imaging}

The goal of all imaging algorithms is to estimate the brightness of the sky $I_\nu(\hat r)$ in the
direction $\hat r$ and frequency $\nu$.  A radio interferometer measures the visibilities
$V^{ij,pq}_{\nu}$ between pairs of antennas numbered $i$ and $j$ respectively, and between
polarizations labeled $p$ and $q$ respectively. We will neglect subtleties associated with polarized
imaging, so the Stokes-$I$ visibilities are constructed from the sum of the $pp$ and $qq$
correlations such that $V^{ij}_{\nu} = (V^{ij,pp}_{\nu}+V^{ij,qq}_{\nu})/2$.  If the antennas are
separated by the baseline $\vec b_{ij}$, and $A_\nu(\hat r)$ describes an antenna's response to the
incident Stokes-$I$ radiation (here assumed to be the same for each antenna), then
\begin{equation}\label{eq:basic-imaging}
    V^{ij}_\nu = \int_\text{sky}
                 A_\nu(\hat r) I_\nu(\hat r)
                 \exp\bigg(2\pi i \hat r\cdot\vec b_{ij}/\lambda\bigg) \,\d\Omega \, ,
\end{equation}
where the integral runs over solid angle $\Omega$.  Constructing an image from the output of a radio
interferometer consists of estimating $I_\nu(\hat r)$ given the available measurements $V^{ij}_\nu$.

For later convenience we will define the baseline transfer function $B^{ij}_\nu(\hat r)$ such that
\begin{equation}\label{eq:baseline-transfer-function}
    V^{ij}_\nu = \int_\text{sky} B^{ij}_\nu(\hat r) I_\nu(\hat r) \,\d\Omega \, .
\end{equation}
The baseline transfer function defines the response of a single baseline to the sky, and is a
function of the antenna primary beam, and baseline length and orientation.

Naively one might attempt to solve Equation~\ref{eq:basic-imaging} by discretizing, and subsequently
solving the resulting matrix equation. If the interferometer is composed of $N_\text{base}$
baselines, and measures $N_\text{freq}$ frequency channels over $N_\text{time}$ integrations, then
the entire data set consists of $N_\text{base}N_\text{freq}N_\text{time}$ complex numbers. If the
sky is discretized into $N_\text{pix}$ pixels then the relevant matrix has dimensions of
$(N_\text{base}N_\text{freq}N_\text{time})\times(N_\text{pix})$. For making single-channel maps with
the OVRO-LWA this becomes a 5 petabyte array (assuming each matrix element is a 64-bit complex
floating point number).  This matrix equation is therefore prohibitively large, and solving
Equation~\ref{eq:basic-imaging} by means of discretization is usually intractable, although
\citet{2017MNRAS.465.2901Z} demonstrate this technique with the MITEOR telescope.

Instead, it is common to make mild assumptions that simplify Equation~\ref{eq:basic-imaging} and
ease the computational burden in solving for $I_\nu(\hat r)$. For example, when all of the baselines
$\vec b_{ij}$ lie in a plane and the field-of-view is small, Equation~\ref{eq:basic-imaging} can be
well-approximated by a two-dimensional Fourier transform \citep{2001isra.book.....T}. The
restriction on baseline co-planarity and field-of-view can be relaxed by using W-projection
\citep{2008ISTSP...2..647C}. Known primary beam effects can also be accounted for during imaging by
using A-projection \citep{2013ApJ...770...91B}.

\subsection{$m$-Mode Analysis}\label{sec:mmode-analysis}

Transit telescopes can take advantage of a symmetry in Equation~\ref{eq:basic-imaging} that greatly
reduces the amount of computer time required to image the full-sky with exact incorporation of
widefield imaging effects. This technique, called $m$-mode analysis, also obviates the need for
gridding and mosaicking. Instead the entire sky is imaged in one coherent synthesis imaging step.  We
will briefly summarize $m$-mode analysis below, but the interested reader should consult
\citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} for a complete derivation.

In the context of $m$-mode analysis, a transit telescope is any interferometer for which the
response pattern of the individual elements does not change with respect to time. This may be an
interferometer like the OVRO-LWA where the correlation elements are fixed dipoles, but it may also
be an interferometer like LOFAR or the MWA if the steerable beams are held in a fixed position (not
necessarily at zenith). The interferometer also does not necessarily have to be homogeneous.
Heterogeneous arrays composed of several different types of antennas are allowed as long as care is
taken to generalize Equation~\ref{eq:basic-imaging} for a heterogeneous array.

For a transit telescope, the visibilities $V^{ij}_\nu$ are a periodic function of sidereal
time.\footnote{
    This is not strictly true. Ionospheric fluctuations and non-sidereal sources (such as the Sun)
    will violate this assumption. This paper will, however, demonstrate that the impact on the final
    maps is mild.
}
Therefore it is a natural operation to compute the Fourier transform of the visibilities with
respect to sidereal time $\phi\in[0,2\pi)$.
\begin{equation}
    V^{ij}_{m,\nu} = \int_0^{2\pi} V^{ij}_\nu(\phi)\exp\bigg(-im\phi\bigg)\,\d\phi
\end{equation}
The output of this Fourier transform is the set of $m$-modes $V^{ij}_{m,\nu}$ where
$m=0,\,\pm1,\,\pm2,\,\ldots$ is the Fourier conjugate variable to the sidereal time. The $m$-mode
corresponding to $m=0$ is a simple average of the visibilities over sidereal time. Similarly $m=1$
corresponds to the component of the visibilities that varies over half-day timescales. Larger values
of $m$ correspond to components that vary on quicker timescales.

\citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} show that there is a discrete linear relationship
between the measured $m$-modes $V^{ij}_{m,\nu}$ and the spherical harmonic coefficients of the sky
brightness $a_{lm,\nu}$.
\begin{equation}\label{eq:m-mode-sum-equation}
    V^{ij}_{m,\nu} = \sum_l B^{ij}_{lm,\nu} a_{lm,\nu}\,,
\end{equation}
where the transfer coefficients $B^{ij}_{lm,\nu}$ are computed from the spherical harmonic transform
of the baseline transfer function defined by Equation~\ref{eq:baseline-transfer-function}. These
transfer coefficients define the interferometer's response to the corresponding spherical harmonic
coefficients.

Equation~\ref{eq:m-mode-sum-equation} can be recognized as a matrix equation where the transfer
matrix $\b B$ is block-diagonal.
\begin{equation}\label{eq:m-mode-matrix-equation}
    \overbrace{\left(
        \begin{array}{c}
            \vdots \\
            m\text{-modes} \\
            \vdots \\
        \end{array}
    \right)}^{\b v}
    =
    \overbrace{\left(
        \begin{array}{ccc}
            \ddots & & \\
            & \text{transfer matrix} & \\
            & & \ddots \\
        \end{array}
    \right)}^{\b B}
    \overbrace{\left(
        \begin{array}{c}
            \vdots \\
            a_{lm} \\
            \vdots \\
        \end{array}
    \right)}^{\b a}
\end{equation}
\begin{equation}
    \b B = \left(\begin{array}{cccc}
        m = 0 &&& \\
              & m=\pm1 && \\
              && m=\pm2 & \\
              &&& \ddots \\
    \end{array}\right)
\end{equation}
The vector $\b v$ contains the list of $m$-modes and the vector $\b a$ contains the list of
spherical harmonic coefficients representing the sky brightness. In order to take advantage of the
block-diagonal structure in $\b B$, $\b v$ and $\b a$ must be sorted by the absolute value of $m$.
Positive and negative values of $m$ are grouped together because the brightness of the sky is
real-valued, and the spherical harmonic transform of a real-valued function has $a_{l(-m)} = (-1)^m
a_{lm}^*$.

@@

The interferometer's sensitivity to the monopole ($a_{00}$) deserves special consideration.
\citet{2016ApJ...826..116V} prove -- under fairly general assumptions -- that a baseline with
nonzero sensitivity to $a_{00}$ must also have some amount of cross-talk or common-mode noise.  In
fact the sensitivity to $a_{00}$ is proportional to a sum of these effects. For example, one way a
baseline can have nonzero sensitivity to $a_{00}$ is if the baseline is extremely short. In this
case the antennas are so close together that voltage fluctuations in one antenna can couple into the
other antenna. In order to make an interferometric measurement of $a_{00}$, this coupling must be
measured and calibrated. Consequently, we set $a_{00}=0$ in our analysis. In the future this
limitation will be addressed with the inclusion of calibrated total power radiometry.

The size of a typical block in the transfer matrix is
$(2N_\text{base}N_\text{freq})\times(l_\text{max})$. If each element of the matrix is stored as a
64-bit complex floating point number, a single block is 500 MB for the case of single-channel
imaging with the OVRO-LWA, which a modern computer can easily store and manipulate in memory.
However, with additional bandwidth these blocks quickly become unwieldy; thus as a first pass, the
analysis in this paper is restricted to single-channel imaging. Note also that for the OVRO-LWA
$N_\text{base} \gg l_\text{max}$, so there are more measurements than unknowns in
Equation~\ref{eq:m-mode-matrix-equation}.

>>>>

\begin{abstract}
    A host of new low-frequency radio telescopes seek to measure the 21~cm transition of neutral
    hydrogen from the early universe.  These telescopes have the potential to directly probe star
    and galaxy formation at redshifts $20 \gtrsim z \gtrsim 7$, but are limited by the dynamic range
    they can achieve against foreground sources of low-frequency radio emission. Consequently, there
    is a growing demand for modern, high-fidelity maps of the sky at frequencies below 200 MHz for
    use in foreground modeling and removal.  We describe a new wide-field imaging technique for
    drift-scanning interferometers: Tikhonov-regularized $m$-mode analysis imaging.  This technique
    constructs images of the entire sky in a single synthesis imaging step with exact treatment of
    wide-field effects.  We describe how the CLEAN algorithm can be adapted to deconvolve maps
    generated by $m$-mode analysis imaging. We demonstrate Tikhonov-regularized $m$-mode analysis
    imaging using the Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA) by generating
    eight new maps of the sky north of $\delta=-30^\circ$ with 15\arcmin angular resolution at
    frequencies evenly spaced between 36.528 and 73.152~MHz, and $\sim$800 mJy/beam thermal noise.
    These maps are a 10-fold improvement in angular resolution over existing full-sky maps at
    comparable frequencies, which have angular resolutions $\ge 2^\circ$. Each map is constructed
    exclusively from interferometric observations and does not represent the globally averaged sky
    brightness. Future improvements will incorporate total power radiometry, improved thermal noise,
    and improved angular resolution due to the planned expansion of the OVRO-LWA to 2.6~km
    baselines.  These maps serve as a first step on the path to the use of more sophisticated
    foreground filters in 21~cm cosmology incorporating the measured angular and frequency structure
    of all foreground contaminants.
\end{abstract}

@@

At redshifts $20 \gtrsim z \gtrsim 7$, the 21~cm hyperfine structure line of neutral hydrogen is
expected to produce a 10 to 100 mK perturbation in the cosmic microwave background (CMB) spectrum
\citep{2006PhR...433..181F, 2012RPPh...75h6901P}. The amplitude of this perturbation on a given line
of sight is a function of the neutral fraction of hydrogen, the baryon overdensity, the spin
temperature relative to the CMB temperature at the given redshift, and the line-of-sight peculiar
velocity of the gas.  The spatial power spectrum of this perturbation is thought to be dominated by
inhomogeneous heating of the intergalactic medium (IGM) at $z\sim 20$ \citep{2014MNRAS.437L..36F},
and by growing ionized bubbles during the epoch of reionization (EoR) at $z\sim 7$, where a
detection can constrain the ionizing efficiency of early galaxies, the UV photon mean-free path, and
the minimum halo mass that can support star formation \citep{2015MNRAS.449.4246G}.

Current 21~cm cosmology experiments can be broadly separated into two classes: global signal
experiments that aim to detect the spectral signature of the cosmologically redshifted 21~cm
transition after averaging over the entire sky (otherwise known as the monopole) and power spectrum
experiments that incorporate angular information to attempt to measure the 3D spatial power spectrum
of cosmological 21~cm perturbations.  Ongoing global signal experiments include EDGES
\citep{2017ApJ...847...64M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS \citep{2015PASA...32....4S},
SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2 \citep{2017arXiv170306647S}.  Ongoing power spectrum
experiments include PAPER/HERA \citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR
\citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B, 2016MNRAS.460.4320E}. Recently,
EDGES reported the first detection of 21~cm absorption in the globally averaged sky signal
\citep{2018Natur.555...67B}.

Just as for CMB experiments, foreground removal or suppression is an essential component of both
classes of 21~cm cosmology experiments. The brightness temperature of the galactic synchrotron
emission at high galactic latitudes is measured by \citet{2017MNRAS.464.4995M} as
\begin{equation}
    T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.6}\,.
\end{equation}
Therefore, experiments conservatively need to achieve five orders of dynamic range against this
foreground emission before the cosmological signal can be measured. Current foreground removal
methods (for example, \citealt{2012ApJ...756..165P} and \citealt{2013MNRAS.429..165C}) rely on the
assumption that the foreground emission is spectrally smooth. The low-frequency radio sky is
composed of several components: galactic synchrotron emission, supernova remnants, radio galaxies,
free-free emission and absorption from \ion{H}{2} regions, and a confusing background of radio
sources.  Ideally, a foreground removal strategy should be informed by the measured spatial
structure and frequency spectrum of all foreground components. For instance, CMB experiments
typically construct several maps at several frequencies to enable component separation.  At low
frequencies, this possibility is limited by the availability of suitable high-fidelity sky maps on
angular scales ranging from tens of degrees to arcminutes.

Recently, a host of new low-frequency sky surveys have been conducted, including MSSS
\citep{2015A&A...582A.123H}, GLEAM \citep{2015PASA...32...25W}, and TGSS
\citep{2017A&A...598A..78I}. However, the primary data product generated by these surveys is a
catalog of radio point sources. At 45 MHz, \citet{2011A&A...525A.138G} created a map of the sky that
captures the diffuse emission with 5$^\circ$ resolution.  The LWA1 Low Frequency Sky Survey
\citep[LLFSS;][]{2017MNRAS.469.4537D} similarly maps the sky at a range of frequencies between
35 and 80~MHz with resolution between 4.5$^\circ$ and 2$^\circ$.

The Global Sky Model \citep[GSM;][]{2008MNRAS.388..247D} is currently the most commonly used
foreground model. The GSM is a nonparametric interpolation of various maps between 10 MHz and 100
GHz. However, the majority of information contained in the GSM is derived at frequencies $>1.4$~GHz,
where the majority of the modern, high-fidelity input maps are located. At 408~MHz, the venerable
Haslam map \citep{1981A&A...100..209H, 1982A&AS...47....1H} covers the entire sky at $1^\circ$
resolution.  Below 408~MHz, the GSM uses three input sky maps. \citet{2017MNRAS.464.3486Z}
constructed an improved GSM with five maps below 408~MHz, and \citet{2017MNRAS.469.4537D} used the
LWA1 to improve the GSM with their own sky maps.  However, the GSM generally suffers from low
angular resolution ($\sim 5^\circ$) and systematic errors associated with instrumental artifacts in
the input maps.  For instance, \citet{2017MNRAS.469.4537D} reported errors of $\pm 50\%$ between the
GSM and their own maps at 74 MHz, which they attribute to the increasing contribution of free-free
absorption and modifications to the synchrotron spectral index at low frequencies.

Wide-field interferometric synthesis imaging is a challenging computational problem, and it has been
particularly difficult to capture large angular scales $\gg 10^\circ$ and small angular scales $\ll
1^\circ$ in a single synthesis image. We will derive a new imaging technique -- Tikhonov-regularized
$m$-mode analysis imaging -- that allows a drift-scanning interferometer to image the entire visible
sky in a single coherent synthesis imaging step with no gridding and no mosaicking.

As a demonstration of this technique, we apply Tikhonov-regularized $m$-mode analysis imaging to the
Owens Valley Radio Observatory Long Wavelength Array (OVRO-LWA) and generate a series of new
low-frequency maps of the sky between 36.528 and 73.152~MHz.  These maps capture the full sky
visible from OVRO with an angular resolution of $\sim 15$~arcmin.  These new maps complement the
existing full-sky maps at these frequencies with greatly improved angular resolution.

We aim for these maps to inform foreground removal strategies in 21~cm cosmology, and we anticipate
additional ancillary science taking advantage of the combination of high fidelity and high
resolution of these maps, including but not limited to studies of the cosmic-ray emissivity at low
frequencies, searches for giant radio galaxies, and constraining the galactic synchrotron spectrum.
The maps will be made freely available online at the Legacy Archive for Microwave Background Data
Analysis (LAMBDA)\footnote{
    \url{https://lambda.gsfc.nasa.gov/product/foreground/fg_ovrolwa_radio_maps_info.cfm}
}.

The structure of this paper is as follows. In \S\ref{sec:imaging}, we present Tikhonov-regularized
$m$-mode analysis imaging, a new imaging technique that allows us to image the entire visible sky in
one coherent synthesis imaging step with exact wide-field corrections. In \S\ref{sec:observations}
we describe our observations with the OVRO-LWA. In \S\ref{sec:results} we present the sky maps and
compare these maps against other low-frequency sky maps.  In \S\ref{sec:error}, we discuss some of
the sources of error present in the maps, and finally, in \S\ref{sec:conclusion} we present our
conclusions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{All-sky Imaging}\label{sec:imaging}

The goal of all imaging algorithms is to estimate the brightness of the sky $I_\nu(\hat r)$ in the
direction $\hat r$ and frequency $\nu$.  A radio interferometer measures the visibilities
$V^{ij,pq}_{\nu}$ between pairs of antennas numbered $i$ and $j$ respectively, and between
polarizations labeled $p$ and $q$ respectively. We will neglect subtleties associated with polarized
imaging, so the Stokes~$I$ visibilities are constructed from the sum of the $pp$ and $qq$
correlations such that $V^{ij}_{\nu} = (V^{ij,pp}_{\nu}+V^{ij,qq}_{\nu})/2$.  If the antennas are
separated by the baseline $\vec b_{ij}$, and $A_\nu(\hat r)$ describes an antenna's response to the
incident Stokes~$I$ radiation (here assumed to be the same for each antenna), then
\begin{equation}\label{eq:basic-imaging}
    V^{ij}_\nu = \int_\text{sky}
                 A_\nu(\hat r) I_\nu(\hat r)
                 \exp\bigg(2\pi i \hat r\cdot\vec b_{ij}/\lambda\bigg) \,\d\Omega \, ,
\end{equation}
where the integral runs over the solid angle $\Omega$.  Constructing an image from the output of a
radio interferometer consists of estimating $I_\nu(\hat r)$ given the available measurements
$V^{ij}_\nu$.

For later convenience, we will define the baseline transfer function $B^{ij}_\nu(\hat r)$ such that
\begin{equation}\label{eq:baseline-transfer-function}
    V^{ij}_\nu = \int_\text{sky} B^{ij}_\nu(\hat r) I_\nu(\hat r) \,\d\Omega \, .
\end{equation}
The baseline transfer function defines the response of a single baseline to the sky and is a
function of the antenna primary beam, and baseline length and orientation.

Naively, one might attempt to solve Equation~\ref{eq:basic-imaging} by discretizing and
subsequently solving the resulting matrix equation. If the interferometer is composed of
$N_\text{base}$ baselines and measures $N_\text{freq}$ frequency channels over $N_\text{time}$
integrations, then the entire data set consists of $N_\text{base}N_\text{freq}N_\text{time}$ complex
numbers. If the sky is discretized into $N_\text{pix}$ pixels, then the relevant matrix has
dimensions of $(N_\text{base}N_\text{freq}N_\text{time})\times(N_\text{pix})$. For making
single-channel maps with the OVRO-LWA, this becomes a 5 PB array (assuming each matrix element
is a 64 bit complex floating point number).  This matrix equation is therefore prohibitively large,
and solving Equation~\ref{eq:basic-imaging} by means of discretization is usually intractable,
although \citet{2017MNRAS.465.2901Z} demonstrated this technique with the MITEOR telescope.

Instead, it is common to make mild assumptions that simplify Equation~\ref{eq:basic-imaging} and
ease the computational burden in solving for $I_\nu(\hat r)$. For example, when all of the baselines
$\vec b_{ij}$ lie in a plane and the field of view is small, Equation~\ref{eq:basic-imaging} can be
well approximated by a two-dimensional Fourier transform \citep{2001isra.book.....T}. The
restriction on baseline coplanarity and field of view can be relaxed by using W-projection
\citep{2008ISTSP...2..647C}. Known primary beam effects can also be accounted for during imaging by
using A-projection \citep{2013ApJ...770...91B}.

\subsection{$m$-mode Analysis}\label{sec:mmode-analysis}

Transit telescopes can take advantage of a symmetry in Equation~\ref{eq:basic-imaging} that greatly
reduces the amount of computer time required to image the full sky with exact incorporation of
wide-field imaging effects. This technique, called $m$-mode analysis, also obviates the need for
gridding and mosaicking. Instead, the entire sky is imaged in one coherent synthesis imaging step.
We will briefly summarize $m$-mode analysis below, but the interested reader should consult
\citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} for a complete derivation.

In the context of $m$-mode analysis, a transit telescope is any interferometer for which the
response pattern of the individual elements does not change with respect to time. This may be an
interferometer like the OVRO-LWA, where the correlation elements are fixed dipoles, but it may also
be an interferometer like LOFAR or the MWA if the steerable beams are held in a fixed position (not
necessarily at zenith). The interferometer also does not necessarily have to be homogeneous.
Heterogeneous arrays composed of several different types of antennas are allowed as long as care is
taken to generalize Equation~\ref{eq:basic-imaging} for a heterogeneous array.

For a transit telescope, the visibilities $V^{ij}_\nu$ are a periodic function of sidereal
time.\footnote{
    This is not strictly true. Ionospheric fluctuations and non-sidereal sources (such as the Sun)
    will violate this assumption. This paper will, however, demonstrate that the impact on the final
    maps is mild.
}
Therefore, it is a natural operation to compute the Fourier transform of the visibilities with
respect to sidereal time $\phi\in[0,2\pi)$.
\begin{equation}
    V^{ij}_{m,\nu} = \int_0^{2\pi} V^{ij}_\nu(\phi)\exp\bigg(-im\phi\bigg)\,\d\phi
\end{equation}
The output of this Fourier transform is the set of $m$-modes $V^{ij}_{m,\nu}$ where
$m=0,\,\pm1,\,\pm2,\,\ldots$ is the Fourier conjugate variable to the sidereal time. The $m$-mode
corresponding to $m=0$ is a simple average of the visibilities over sidereal time. Similarly, $m=1$
corresponds to the component of the visibilities that varies over half-day timescales. Larger values
of $m$ correspond to components that vary on quicker timescales.

\citet{2014ApJ...781...57S, 2015PhRvD..91h3514S} showed that there is a discrete linear relationship
between the measured $m$-modes $V^{ij}_{m,\nu}$ and the spherical harmonic coefficients of the sky
brightness $a_{lm,\nu}$.
\begin{equation}\label{eq:m-mode-sum-equation}
    V^{ij}_{m,\nu} = \sum_l B^{ij}_{lm,\nu} a_{lm,\nu}\,,
\end{equation}
where the transfer coefficients $B^{ij}_{lm,\nu}$ are computed from the spherical harmonic transform
of the baseline transfer function defined by Equation~\ref{eq:baseline-transfer-function}. These
transfer coefficients define the interferometer's response to the corresponding spherical harmonic
coefficients.

Equation~\ref{eq:m-mode-sum-equation} can be recognized as a matrix equation, where the transfer
matrix $\b B$ is block-diagonal:
\begin{equation}\label{eq:m-mode-matrix-equation}
    \overbrace{\left(
        \begin{array}{c}
            \vdots \\
            m\text{-modes} \\
            \vdots \\
        \end{array}
    \right)}^{\b v}
    =
    \overbrace{\left(
        \begin{array}{ccc}
            \ddots & & \\
            & \text{transfer matrix} & \\
            & & \ddots \\
        \end{array}
    \right)}^{\b B}
    \overbrace{\left(
        \begin{array}{c}
            \vdots \\
            a_{lm} \\
            \vdots \\
        \end{array}
    \right)}^{\b a}
\end{equation}
\begin{equation}
    \b B = \left(\begin{array}{cccc}
        m = 0 &&& \\
              & m=\pm1 && \\
              && m=\pm2 & \\
              &&& \ddots \\
    \end{array}\right)
\end{equation}
The vector $\b v$ contains the list of $m$-modes and the vector $\b a$ contains the list of
spherical harmonic coefficients representing the sky brightness. In order to take advantage of the
block-diagonal structure in $\b B$, $\b v$ and $\b a$ must be sorted by the absolute value of $m$.
Positive and negative values of $m$ are grouped together because the brightness of the sky is
real-valued, and the spherical harmonic transform of a real-valued function has $a_{l(-m)} = (-1)^m
a_{lm}^*$.

@@

The interferometer's sensitivity to the monopole ($a_{00}$) deserves special consideration.
\citet{2016ApJ...826..116V} proveed -- under fairly general assumptions -- that a baseline with
nonzero sensitivity to $a_{00}$ must also have some amount of cross-talk or common-mode noise.  In
fact, the sensitivity to $a_{00}$ is proportional to a sum of these effects. For example, one way a
baseline can have nonzero sensitivity to $a_{00}$ is if the baseline is extremely short. In this
case, the antennas are so close together that voltage fluctuations in one antenna can couple into the
other antenna. In order to make an interferometric measurement of $a_{00}$, this coupling must be
measured and calibrated. Consequently, we set $a_{00}=0$ in our analysis. In the future, this
limitation will be addressed with the inclusion of calibrated total power radiometry.

The size of a typical block in the transfer matrix is
$(2N_\text{base}N_\text{freq})\times(l_\text{max})$. If each element of the matrix is stored as a
64 bit complex floating point number, a single block is 500 MB for the case of single-channel
imaging with the OVRO-LWA, which a modern computer can easily store and manipulate in memory.
However, with additional bandwidth, these blocks quickly become unwieldy; thus, as a first pass, the
analysis in this paper is restricted to single-channel imaging. Note also that for the OVRO-LWA,
$N_\text{base} \gg l_\text{max}$, so there are more measurements than unknowns in
Equation~\ref{eq:m-mode-matrix-equation}.
